General writeup

### 2017-11-27 Latex/general_writeup.tex
1.11 Another specification in line with 1.4 and 1.6
 in line with 1.4 and 1.6. Also impact of relative prices is significan for both shocks

>>>>

\newpage
\subsection{Relative prices LR horizon 8}

\input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}

\begin{figure}[h!]
	\centering
	\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_27-Nov-2017_14_42_29}} \hspace{.2in%
	} 
	\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_27-Nov-2017_14_42_32}}
\end{figure}
